\documentclass[11pt,a4paper]{article}

\usepackage[a4paper,margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{array}

\pagenumbering{gobble}

\titleformat{\section}
{\large\bfseries}
{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE \textbf{Amrita Kumari}}\\[4pt]
    \textbf{Frontend Web Developer}\\[6pt]

    \href{mailto:dev.amritasrc@gmail.com}{dev.amritasrc@gmail.com} \quad | \quad
    \href{https://linkedin.com/in/yourusername}{LinkedIn} \quad | \quad
    \href{https://github.com/amritasrc}{GitHub} \quad | \quad
    \href{https://yourportfolio.com}{Portfolio}\\
    Ranchi, India
\end{center}

%----------------------------------------

\section*{Professional Summary}

Frontend-focused web developer with experience building dynamic applications using JavaScript, React, HTML, and CSS. Skilled in API integration, DOM manipulation, and developing practical solutions such as browser extensions. Passionate about modern web development and creating clean, user-friendly interfaces.

%----------------------------------------

\section*{Education}

\textbf{Jharkhand Rai University}, Ranchi\\
Bachelor of Technology in Computer Science and Engineering\\
Sep 2024 -- Sep 2028 \hfill \textbf{CGPA: 9.09}

%----------------------------------------

\section*{Projects}

\textbf{CopyIt} \hfill Jul 2026

\begin{itemize}[leftmargin=*]
\item Developed a Code Snippet Vault using React.js, Tailwind CSS, and Monaco Editor, enabling users to create, edit, organize, and manage reusable code snippets.
\item Integrated Monaco Editor with CRUD operations, syntax highlighting, language selection, keyword search, and responsive UI.
\item \textbf{Tech Stack:} React, Tailwind CSS, JavaScript
\end{itemize}

\vspace{4pt}

\textbf{Rhythmify} \hfill Jun 2026

\begin{itemize}[leftmargin=*]
\item Developed a React-based music player integrating the YouTube Data API to search and stream songs.
\item Built custom media controls with play/pause, seek, keyboard shortcuts, and responsive playback.
\item \textbf{Tech Stack:} React, Tailwind CSS, JavaScript
\end{itemize}

\vspace{4pt}

\textbf{GitProfile} \hfill Jun 2026

\begin{itemize}[leftmargin=*]
\item Built a GitHub Profile Search application using React.js, Tailwind CSS, and the GitHub REST API.
\item Displayed real-time GitHub profile and repository information with optimized API requests and responsive UI.
\item \textbf{Tech Stack:} React, Tailwind CSS, JavaScript, GitHub API
\end{itemize}

\vspace{4pt}

\textbf{YouTube Study Mode (Chrome Extension)} \hfill May 2026

\begin{itemize}[leftmargin=*]
\item Built a Chrome extension that blocks distracting YouTube elements using DOM manipulation and CSS.
\item Used content scripts to maintain focus mode across navigation.
\item \textbf{Tech Stack:} JavaScript, HTML, CSS, Chrome Extensions API
\end{itemize}

%----------------------------------------

\section*{Skills}

\begin{tabular}{>{\bfseries}p{4cm}p{11cm}}

Programming Languages & C, C++, Java, Python, JavaScript \\

Frontend & React.js, HTML5, CSS3, Tailwind CSS, Framer Motion \\

Database & Supabase \\

Tools & Git, GitHub, Monaco Editor \\

Languages & English, Hindi \\

Soft Skills & Communication, Leadership, Critical Thinking, Decision Making, Problem Solving \\

\end{tabular}

\end{document}